Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-10-06 main.tex
work on introduction

\begin{abstract}
    We construct potentials for the gradient, the curl, and the divergence operators over domains with shellable triangulations. 
    The operator norms of our potentials satisfy explicitly computable bounds that depend only on the geometry. 
    We thus obtain computable upper bounds for constants in Poincar\'e--Friedrichs inequalities as well as computable lower bounds for the eigenvalues of several vector Laplacians. 
    % We derive computable bound on the operator norms of our potentials that only depend on the geometry. 
    Importantly, the class of shellable triangulations includes local patches (stars) in two or three dimensions. 
    % 
    %     We construct upper bounds for Poincar\'e--Friedrichs constants over triangulated domains. 
    %     This includes lower estimates for the singular values of the gradient, curl, and divergence operators as special cases. 
    %     The main application that we envision are computable estimates over finite element patches. 
    %
    As a result with independent standing, we also establish Poincar\'e--Friedrichs inequalities with computable constants for the $L^{p}$ de~Rham complex over convex bounded domains. 
    This is achieved via a suitable construction of regularized Poincar\'e and Bogovski\u{\i} potential operators whose operator norms we bound.
    \mwl{We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances.} 
    Computational examples illustrate the theoretical findings.
\end{abstract}

@@

Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance. The operator norms of the\cye{se} potentials are upper bounds for the Poincar\'e--Friedrichs constants, which quantify the fundamental stability features of a variety of partial differential equations. In numerical methods, estimates for the Poincar\'e--Friedrichs constant\cye{s} enter the stability and convergence theory and spectral bounds for \cye{stiffness} matrices. \cye{Computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians}. However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study, quantifiable results regarding the curl and divergence operators or \cye{more generally} the exterior derivative are \cye{largely unavailable}.

\cye{Our main purpose here is to fill this gap. In the gradient case, we can go over with so-called face-connected triangulations. However, to proceed} in the \cye{general exterior derivative case, we are brought to} so-called shellable triangulations. 
Even though only contractible domains can ever admit a shellable triangulation, 
having computable upper bounds for such domains is an important stepping stone towards more general cases. \cye{Still, we cover most practical non-convex and non-star-shaped triangulated domains, and as a particular example, local triangulations} around a simplex within a larger triangulation \cye{(the so-called local patches or stars), which are} shellable in two and three spaces dimensions. \cye{Over convex bounded domains, we derive Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex.}

@@

\subsection{\cye{Potential for the gradient operator and the corresponding Poincar\'e--Friedrichs inequality}} \label{subsection:intro_grad}

@@

\subsection{\cye{Potentials for the curl and divergence operators and the corresponding Poincar\'e--Friedrichs inequalities}} \label{section:intro_curl_div}

@@

\subsection{\cye{Potentials for the exterior derivative and the corresponding Poincar\'e--Fried\-richs inequalities}} \label{section:intro_EC}

@@

\subsection{\cye{Numerically computed guaranteed bounds on Poincar\'e--Friedrichs constants seen as eigenvalues}}

@@

\subsection{\cye{Objectives and methodology}}

@@

\subsubsection{\cye{Combinatorial constants over face-connected triangulated domains}}

@@

\subsubsection{\cye{Combinatorial constants over shellable triangulated domains}}

@@

\subsubsection{\cye{Analytical constants over convex domains}}

\cye{We devote a considerable effort to convex domains for two reasons: first, they are evidently of independent interest, and second, we need them as a building block for the above-discussed recursive procedures on general (non-convex and non-star-shaped) triangulated domains. Here,} we follow closely the \cye{concepts of} Costabel and McIntosh~\cite{costabel2010bogovskiui} who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators. In comparison to their exposition, \cye{which allows for} domains star-shaped with respect to a ball, the regularized potential operators we propose are simplified: we only study them over convex domains and use simpler (constant) weight functions. 
The resulting operator features generally lower regularity \cye{but} its properties are sufficient for our purposes. \cye{Crucially, this allows us to} easily estimate their operator norms.

\subsubsection{\cye{Domains star-shaped with respect to a ball}}

\cye{Let us only briefly discuss why don't we treat local \cye{patches} (stars) in triangulations as} domains star-shaped with respect to a ball, which they are. This \cye{would enable} the use of averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}. Unfortunately, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
This \cye{would not be} as much a problem over local patches (stars) around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
\cye{Unfortunately,} the interior ball can be arbitrarily small when the local patch is around a boundary simplex, even if the mesh has good shape regularity: 
this \cye{in particular} occurs when the domain has sharp reentrant corners. Some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed}, 
which contain local finite element patches \cye{that} are not star-shaped with respect to any ball.

\subsubsection{\cye{Potentials subject to partial boundary conditions}}

\cye{In our proofs for triangulated domains}, we \cye{actually also} need to find potentials for the gradient, curl, and divergence operators\cye{, and in general the exterior derivative,} over a simplex subject to partial boundary conditions. 
Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
We are not aware of explicit estimates in the literature and \cye{we know} no regularized potential operators for these boundary conditions. 
\cye{Our basic idea here is to reuse} the Poincar\'e--Friedrichs inequalities subject to boundary conditions \cye{on the entire boundary in order} to prove Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions. 
For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces. We achieve this by \cye{an affine ``symmetrization'' map of the tetrahedron to a domain consisting of two tetrahedra,} construction of an auxiliary problem subject to full boundary conditions, and then affine ``folder'' map back to the tetrahedron.

\subsection{\cye{Main results}}

@@

Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance.
The operator norms of the potentials are upper bounds for the Poincar\'e--Friedrichs constants, 
which quantify the fundamental stability features of a variety of partial differential equations.
However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study, quantifiable results regarding the curl and divergence operators or the exterior derivative are not nearly as numerous yet.

Domains that admit finite triangulations allow for different techniques to attain Poincar\'e--Friedrichs inequalities. 
However, the majority of results only address such inequalities for scalar-valued functions, not for vector fields. 
We review some of the main outcomes. 
Veeser and Verf\"urth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}. Naturally, their estimate deteriorates when the shape regularity of the mesh deteriorates. 
% 
The literature~\cite{Eym_Gal_Her_00,vohralik2005discrete,ern2020stable,ern2021finite,Chaum_Voh_p_rob_3D_H_curl_23,Voh_loc_glob_H1_24} knows different variations of a popular avenue towards Poincar\'e--Friedrichs constants that circumvents the effect of low boundary regularity and constructs potentials step-by-step: 
starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is exhausted. That procedure applies to general triangulated domains, not only local stars, though the latter is our main interest here. 
The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
along the interfacing intersection, the two potentials will only differ by a constant, 
and that difference can easily be removed to ensure continuity across that interface.

@@

% General outline 
We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence. The basic inductive strategy remains the same. We start by constructing, say, a curl potential, over a single simplex. Having already defined a potential operator over a subtriangulation, we then construct a potential over a neighboring simplex. However, the two potentials might not have the same tangential trace along the interface between the subtriangulation and the new simplex. 
% 
To ensure the correct continuity properties, we require stronger conditions on the triangulations than in the case of gradient potentials. We postulate that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex. Under those conditions, which are met by so-called \textit{shellable} triangulations, we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions. Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
\\

Shellable triangulations are defined by a special constructive property:
we can assemble such triangulations sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler1995lectures}, which we only employ in a simple special case. 
In particular, local stars in 2D and 3D triangulations are shellable. 
\\

\paragraph{Notation}

\mwl{Fix this}
Given a matrix $A \in \bbR^{n \times n}$, we let $\sigma_{1}(A) \geq \dots \geq \sigma_{n}(A) \geq 0$ denote the descending sequence of its singular values, 
where $\sigma_{\max}(A) := \sigma_{1}(A)$ is the largest and $\sigma_{\min}(A) := \sigma_{n}(A)$ is the smallest. 
We recall that the $\ell^{2}$ operator norm of $A$, written $\| A \|_{2}$, agrees with $\sigma_{\max}(A)$,
and if $A$ is invertible, then $\|A^{-1}\| = \sigma_{\min}(A)^{-1}$.
% Another norm on matrices, less common but useful for us, is the \emph{maximum column norm} $\|A\|_{\maxcol}$, which is defined as the largest $\ell^{2}$-norm of any column of $A$.

@@

%\mwl{In what follows, $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.}
Let $\Omega \subseteq \bbR^{n}$ is a convex bounded open set with diameter $\diam(\Omega) > 0$.

@@

\begin{theorem}\label{theorem:bogovpoinc}
    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set and let $1 \leq p \leq \infty$. 
    We have bounded operators 
    \begin{align*}
        \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}\Alt^{\mia-1}(\Omega)
        ,
        \qquad 
        \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\mia-1}(\Omega)
        .
    \end{align*}
    They satisfy the operator norm bounds 
    \begin{align*}
        \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
        &\leq 
        n C_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
        \diam(\Omega)
        \| u \|_{L^{p}(\Omega)}
        ,
        \\
        \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
        &\leq 
        n C_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
        \diam(\Omega)
        \| u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    For any $u \in \bfW^{p}\Alt^{\mia}(\Omega)$ it holds that 
    \begin{align}
        u(x) &= \Poinc_{1} \cartan u(x) - \vol(\Omega)^{-1} \int_\Omega u(a) \;da
        \label{math:theorem:bogovpoinc:poincare:zero}
        \\
        u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 1 \leq \mia \leq n.
        \label{math:theorem:bogovpoinc:poincare:k}
    \end{align}
    In particular, if $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Poinc_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.

@@

    {\color{blue}
    Costabel and McIntosh~\cite{costabel2010bogovskiui} regularize the potentials by averaging over pivot points within an interior ball using a smooth compactly supported weight function, 
    which is why they can study domains star-shaped with respect to a ball. 
    Their operators are pseudo-differential operators of negative order, 
    because their averaging uses a smooth weight; this proves that the operators are bounded between a variety of function spaces. 
    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
    have been recently contributed by Guzman and Salgado~\cite{guzman2021estimation}. 
    Instead, we average over the entire domain, which requires a convex geometry, and we are only interested in boundedness in the Lebesgue $p$ norms. 
    Crucially, this exactly allows us to easily establish computable bounds on the Poincar\'e--Friedrichs constants.   
    This had not been established yet, to the best of our knowledge. 
    }
\end{remark}

@@

\begin{lemma}\label{lemma:PFexteriorsimplex}
    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set. 
    Let $0 \leq k < n$. 
    Then for each $u \in W^{p}\Lambda^{k}(\Omega)$ 
    there exists $w \in W^{p}\Lambda^{k}(\Omega)$ 
    with $\cartan u = \cartan w$ and 
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}
        &
        \leq 
        C_{{\PF},k,\Omega,p}
        \| \cartan u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    where 
    \begin{align*}
        C_{{\PF},k,\Omega,p} 
        = 
        n C_{\Poinc}(n,k+1) 
        \vol_{}(B_1(0)) 
        \frac{ \diam(\Omega)^{n} }{ \vol(\Omega) } 
        \diam(\Omega)
        .
    \end{align*}
\end{lemma}
\begin{proof}
    This follows from Theorem~\ref{theorem:bogovpoinc} using $\vol(B_{\diam(\Omega)}(0)) = \vol_{}(B_1(0)) \diam(\Omega)^{n}$.
\end{proof}

>>>>

\begin{abstract}
    We construct potentials for the gradient, the curl, and the divergence operators over domains with shellable triangulations. 
    The operator norms of our potentials satisfy explicitly computable bounds that depend only on the geometry. 
    We thus obtain computable upper bounds for constants in Poincar\'e--Friedrichs inequalities as well as computable lower bounds for the eigenvalues of several vector Laplacians. 
    % We derive computable bound on the operator norms of our potentials that only depend on the geometry. 
    Importantly, the class of shellable triangulations includes local patches (stars) in two or three dimensions. 
    % 
    %     We construct upper bounds for Poincar\'e--Friedrichs constants over triangulated domains. 
    %     This includes lower estimates for the singular values of the gradient, curl, and divergence operators as special cases. 
    %     The main application that we envision are computable estimates over finite element patches. 
    %
    As a result with independent standing, we also establish Poincar\'e--Friedrichs inequalities with computable constants for the $L^{p}$ de~Rham complex over bounded convex domains. 
    This is achieved via a suitable construction of regularized Poincar\'e and Bogovski\u{\i} potential operators whose operator norms we bound.
    \mwl{We express all our main results in the calculus of differential forms and treat the gradient, curl, and divergence operator as its particular instances.} 
    Computational examples illustrate the theoretical findings.
\end{abstract}

@@

Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance. 
The operator norms of these potentials are upper bounds for the Poincar\'e--Friedrichs constants, 
which quantify the fundamental stability features of a variety of partial differential equations. 
In numerical methods, estimates for the Poincar\'e--Friedrichs constants enter the stability and convergence theory and spectral bounds for stiffness matrices. 
Computable upper bounds on the Poincar\'e--Friedrichs constants also give computable lower bounds for the eigenvalues of the associated Laplacians. 
However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study,
quantifiable results regarding the curl and divergence operators, or more generally the exterior derivative, are largely unavailable.

This manuscript aims to fill this gap. \cye{In the gradient case, we can go over with so-called face-connected triangulations. However, to proceed in the general exterior derivative case, we are brought to so-called shellable triangulations.} 
Even though only contractible domains can ever admit a shellable triangulation, 
having computable upper bounds for such domains is an important stepping stone towards more general cases. \cye{We cover most practical non-convex and non-star-shaped triangulated domains,} and as a particular example, local triangulations around a simplex within a larger triangulation (the so-called local patches or stars), which are shellable in two and three spaces dimensions. Additionally, we derive Poincar\'e--Friedrichs inequalities with computable constants for the whole $L^{p}$ de~Rham complex over bounded convex domains.

% old
Potentials for the differential operators of vector calculus and exterior calculus are of fundamental importance.
The operator norms of the potentials are upper bounds for the Poincar\'e--Friedrichs constants, 
which quantify the fundamental stability features of a variety of partial differential equations.
However, while potential operators and Poincar\'e--Friedrichs constants for the gradient have been subject to extensive study, quantifiable results regarding the curl and divergence operators or the exterior derivative are not nearly as numerous yet.

\subsection{Conceptual overview: gradient}

\subsection{Conceptual overview: Potential for the gradient operator and the corresponding Poincar\'e--Friedrichs inequality} \label{subsection:intro_grad}

@@

@@

\subsection{Conceptual overview: Potentials for the curl and divergence operators and the corresponding Poincar\'e--Friedrichs inequalities} \label{section:intro_curl_div}

@@

\subsection{Conceptual overview: curl, divergence, exterior derivative}

\subsection{Conceptual overview: Potentials for the exterior derivative and the corresponding Poincar\'e--Fried\-richs inequalities} \label{section:intro_EC}

@@

\subsection{Review: Analytical constants over convex domains}

\cye{We devote a considerable effort to convex domains for two reasons: first, they are evidently of independent interest, and second, we need them as a building block for the above-discussed recursive procedures on general (non-convex and non-star-shaped) triangulated domains. Here,} we follow closely the \cye{concepts of} Costabel and McIntosh~\cite{costabel2010bogovskiui} who study regularized Poincar\'e and Bogovski\u{\i}-type potential operators. In comparison to their exposition, \cye{which allows for} domains star-shaped with respect to a ball, the regularized potential operators we propose are simplified: we only study them over convex domains and use simpler (constant) weight functions. 
The resulting operator features generally lower regularity \cye{but} its properties are sufficient for our purposes. \cye{Crucially, this allows us to} easily estimate their operator norms. 
\\

\subsection{Review: Domains star-shaped with respect to a ball}

\cye{Let us only briefly discuss why don't we treat local \cye{patches} (stars) in triangulations as} domains star-shaped with respect to a ball, which they are. This \cye{would enable} the use of averaged Poincar\'e and Bogovski\u{\i} operators~\cite{costabel2010bogovskiui}. Unfortunately, estimates that rely on this geometric condition deteriorate when the aforementioned ball has radius much smaller than the domain diameter. 
This \cye{would not be} as much a problem over local patches (stars) around interior subsimplices, where the size of the interior ball only depends on the shape regularity of the triangulation. 
\cye{Unfortunately,} the interior ball can be arbitrarily small when the local patch is around a boundary simplex, even if the mesh has good shape regularity: 
this \cye{in particular} occurs when the domain has sharp reentrant corners. Some illustrative limit cases include the slit domain~\cite{veeser2012poincare} and the crossed bricks domain~\cite{licht2019smoothed}, 
which contain local finite element patches \cye{that} are not star-shaped with respect to any ball. 
\\

\subsection{Review: Potentials subject to partial boundary conditions}

\cye{In our proofs for triangulated domains}, we \cye{actually also} need to find potentials for the gradient, curl, and divergence operators\cye{, and in general the exterior derivative,} over a simplex subject to partial boundary conditions. 
Again, we want to address the entire range $1 \leq p \leq \infty$ of Lebesgue exponents. 
We are not aware of explicit estimates in the literature and \cye{we know} no regularized potential operators for these boundary conditions. 
\cye{Our basic idea here is to reuse} the Poincar\'e--Friedrichs inequalities subject to boundary conditions \cye{on the entire boundary in order} to prove Poincar\'e--Friedrichs inequalities over simplices and subject to partial boundary conditions. 
For example, given a divergence-free vector field over a tetrahedron with vanishing normal trace along three of the tetrahedron's faces, we want to find the unique vector field potential that is the preimage under the curl operator and which has vanishing tangential trace along the same three faces. We achieve this by \cye{an affine ``symmetrization'' map of the tetrahedron to a domain consisting of two tetrahedra,} construction of an auxiliary problem subject to full boundary conditions, and then affine ``folder'' map back to the tetrahedron.
\\

\subsection{Objectives: convex domains}

\subsection{Review: Numerically computed guaranteed bounds on Poincar\'e--Friedrichs constants seen as eigenvalues}

@@

\subsection{Objectives and methodology}

@@

\subsection{Combinatorial constants over face-connected triangulated domains}

@@

\subsection{Combinatorial constants over shellable triangulated domains}

@@

\subsection{Main results}

@@

\subsection{Review: Triangulated domains}

Domains that admit finite triangulations allow for different techniques to attain Poincar\'e--Friedrichs inequalities. 
However, the majority of results only address such inequalities for scalar-valued functions, not for vector fields. 
We review some of the main outcomes. 
Veeser and Verf\"urth provide computable upper bounds in the case of the classical Sobolev space $W^{1,p}(\Omega)$ over triangulated domains, with focus on efficient estimates for finite element stars~\cite{veeser2012poincare}. Naturally, their estimate deteriorates when the shape regularity of the mesh deteriorates.

The literature~\cite{Eym_Gal_Her_00,vohralik2005discrete,ern2020stable,ern2021finite,Chaum_Voh_p_rob_3D_H_curl_23,Voh_loc_glob_H1_24} knows different variations of a popular avenue towards Poincar\'e--Friedrichs constants that circumvents the effect of low boundary regularity and constructs potentials step-by-step: 
starting with a single triangle, the potential is constructed over increasing subdomains, until the entire domain is exhausted. 
That procedure applies to general triangulated domains, not only local stars, though the latter is our main interest here. 
The underlying idea is that we first construct a potential for the gradient over an initial simplex. 
Every time we have found a potential over a subdomain, we construct a potential over a neighboring simplex or patch:
along the interfacing intersection, the two potentials will only differ by a constant, 
and that difference can easily be removed to ensure continuity across that interface.

@@

\subsection{Objective: sequential approach} 
We want to generalize the sequential construction of the potential operator for the gradient to vector potentials for the curl and divergence. The basic inductive strategy remains the same. We start by constructing, say, a curl potential, over a single simplex. Having already defined a potential operator over a subtriangulation, we then construct a potential over a neighboring simplex. However, the two potentials might not have the same tangential trace along the interface between the subtriangulation and the new simplex. 
% 
To ensure the correct continuity properties, we require stronger conditions on the triangulations than in the case of gradient potentials. We postulate that the intermediate subtriangulations are manifolds with boundary, and that the aforementioned interface is, more specifically, a boundary submanifold of the intermediate subtriangulation and the new simplex. Under those conditions, which are met by so-called \textit{shellable} triangulations, we define a well-posed auxiliary problem for the curl operator with partial tangential boundary conditions. Repeating this procedure exhausts the original triangulation and eventually provides the desired potential.
\\

\subsection{Objective: shellable triangulations}
Shellable triangulations are defined by a special constructive property:
we can assemble such triangulations sequentially, adding one simplex after another, such that the interface between the previous intermediate triangulation and the next simplex is always a boundary submanifold of both.
Loosely speaking, this guarantees that the interface with each successive simplex is sufficiently well-behaved.
Shellability of simplicial complexes and, more generally, of polytopal complexes is a well-established notion in discrete geometry and combinatorics~\cite{ziegler1995lectures}, which we only employ in a simple special case. 
In particular, local stars in 2D and 3D triangulations are shellable. 
\\

\subsection{Notation}

Whenever $x \in \bbR^{n}$ is a vector, we write $\|x\| = \|x\|_{2}$ for its Euclidean norm, 
and whenever $A \in \bbR^{n \times n}$, we let $\| A \|_{2}$ be its operator norm with respect to the Euclidean norm. 
Furthermore, $\Jacobian F$ always denotes the Jacobian of any mapping $F$.

@@

%\mwl{In what follows, $\Omega \subseteq \bbR^{n}$ is a bounded convex open set with diameter $\diam(\Omega) > 0$.}
Let $\Omega \subseteq \bbR^{n}$ is a bounded convex open set with diameter $\diam(\Omega) > 0$.

@@

\begin{theorem}\label{theorem:bogovpoinc}
    Let $\Omega \subseteq \bbR^{n}$ be a bounded convex open set and let $1 \leq p \leq \infty$. 
    We have bounded operators 
    \begin{align*}
        \Poinc_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}\Alt^{\mia-1}(\Omega)
        ,
        \qquad 
        \Bogov_{\mia} : L^{p}\Alt^{\mia}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\mia-1}(\Omega)
        .
    \end{align*}
    They satisfy the operator norm bounds 
    \begin{align*}
        \| \Poinc_{\mia} u \|_{L^{p}(\Omega)}
        &\leq 
        n C_{\Poinc}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
        \diam(\Omega)
        \| u \|_{L^{p}(\Omega)}
        ,
        \\
        \| \Bogov_{\mia} u \|_{L^{p}(\Omega)}
        &\leq 
        n C_{\Bogov}(n,\mia) \frac{ \vol_{}(B_{\diam(\Omega)}(0)) }{\vol(\Omega)} 
        \diam(\Omega)
        \| u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    For any $u \in \bfW^{p}\Alt^{\mia}(\Omega)$ it holds that 
    \begin{align}
        u(x) &= \Poinc_{1} \cartan u(x) - \vol(\Omega)^{-1} \int_\Omega u(a) \;da
        \label{math:theorem:bogovpoinc:poincare:zero}
        \\
        u(x) &= \cartan \Poinc_{\mia} u(x) + \Poinc_{\mia+1} \cartan u(x), \qquad 1 \leq \mia \leq n.
        \label{math:theorem:bogovpoinc:poincare:k}
    \end{align}
    In particular, if $u \in W^{p}    \Alt^{\mia}(\Omega)$ with $0 \leq \mia \leq n-1$, then $w = \Poinc_{\mia} \cartan u$ satisfies $\cartan w = \cartan u$.

@@

    \mwl{ 
    Costabel and McIntosh~\cite{costabel2010bogovskiui} regularize the potentials by averaging over pivot points within an interior ball using a smooth compactly supported weight function, 
    which is why they can study domains star-shaped with respect to a ball. 
    Their operators are pseudo-differential operators of negative order, 
    because their averaging uses a smooth weight; this proves that the operators are bounded between a variety of function spaces. 
    Explicit bounds for the higher-order seminorms of these pseudo-differential operators 
    have been recently contributed by Guzman and Salgado~\cite{guzman2021estimation}. 
    Instead, we average over the entire domain, which requires a convex geometry, and we are only interested in boundedness in the Lebesgue $p$ norms. 
    Crucially, this exactly allows us to easily establish computable bounds on the Poincar\'e--Friedrichs constants.   
    This had not been established yet, to the best of our knowledge. 
    }
\end{remark}

@@

\begin{lemma}\label{lemma:PFexteriorsimplex}
    Let $\Omega \subseteq \bbR^{n}$ be a bounded convex open set. 
    Let $0 \leq k < n$. 
    Then for each $u \in W^{p}\Lambda^{k}(\Omega)$ 
    there exists $w \in W^{p}\Lambda^{k}(\Omega)$ 
    with $\cartan u = \cartan w$ and 
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}
        &
        \leq 
        C_{{\PF},k,\Omega,p}
        \| \cartan u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    where 
    \begin{align*}
        C_{{\PF},k,\Omega,p} 
        = 
        n C_{\Poinc}(n,k+1) 
        \vol_{}(B_1(0)) 
        \frac{ \diam(\Omega)^{n} }{ \vol(\Omega) } 
        \diam(\Omega)
        .
    \end{align*}
\end{lemma}
\begin{proof}
    This follows from Theorem~\ref{theorem:bogovpoinc} using $\vol(B_{\diam(\Omega)}(0)) = \vol_{}(B_1(0)) \diam(\Omega)^{n}$.
\end{proof}
